### 2017-04-25 R/ITHIM.Rmd
Changed state ITHIM list to use deciles instead of percentiles
Fixed a few bugs
Most of the problem is with external data.  Need to improve that.

NHTS.person <- with(PERV2PUB,{
                    data.frame(HOUSEID = HOUSEID,
                               PERSONID = PERSONID,
                               SEX = as.factor(ifelse(R_SEX=="1", "M", ifelse(R_SEX=="2", "F", NA))),
                               AGE = as.factor(convertToAgeClass(R_AGE)),
                               MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                               HHSTATE = as.character(HHSTATE),
                               HHS = as.character(convertToHHS(as.character(HHSTATE))), stringsAsFactors = FALSE

@@

```{r loadNHTS, eval = !compute}
NHTS <- readRDS(file = "./data/NHTS.rds")
```

@@

```{r newMETs, echo = TRUE, eval = TRUE, echo = FALSE}
newMETsFile <- "ATUS_to_METS_key.csv"

newMETsFile <- system.file(newMETsFile, package="ITHIM")

@@

gbdRDS <-  readRDS(file = "./data/stateMetroBurdens2014.rds")
gbdRDS <- within(gbdRDS, state <- stateNameToAbbrev(state))

@@

ITHIM.default <- update(ITHIM.default, list( cvNonTravel = 3, cv = 1.65, muNonTravel = 4, muNonTravelMatrix = METmatrix, quantiles = (1:99)/100 ) )

>>>>

NHTS.person <- with(PERV2PUB,{
                    data.frame(HOUSEID = HOUSEID,
                               PERSONID = PERSONID,
                               SEX = as.factor(ifelse(R_SEX=="1", "M", ifelse(R_SEX=="2", "F", NA))),
                               AGE = as.factor(ITHIM:::convertToAgeClass(R_AGE)),
                               MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                               HHSTATE = as.character(HHSTATE),
                               HHS = as.character(convertToHHS(as.character(HHSTATE))), stringsAsFactors = FALSE

@@

```{r loadNHTS, eval = !compute}
NHTS <- readRDS(file = "~/GHI/R/data/NHTS.rds")
```

@@

```{r newMETs, echo = TRUE, eval = TRUE, echo = FALSE}
newMETsFile <- "~/GHI/data/ATUS_to_METS_key.csv"

#newMETsFile <- system.file(newMETsFile, package="ITHIM")

@@

gbdRDS <-  readRDS(file = "~/GHI/R/data/stateMetroBurdens2014.rds")
gbdRDS <- within(gbdRDS, state <- stateNameToAbbrev(state))

@@

ITHIM.default <- update(ITHIM.default, list( cvNonTravel = 3, cv = 1.65, muNonTravel = 4, muNonTravelMatrix = METmatrix, quantiles = (1:9)/10 ) )
